Measuring causal influence with\\ back-to-back regression

### 2019-05-22 paper/paper.tex
Sync

\title{Discovering causal factors with back-to-back regression}

@@

    \node[] (labY) at (\posY, 2){Observations};
    \node[] (labX) at (\posX, 2){Factors};
    \node[] (labE) at (\posE, 2.3){Cause};
    \node[] (labE) at (\posE, 2){selection};
    \node[] (labN) at (\posN, 2){Noise};
    \node[] (labF) at (\posF, 2.3){Cause-effect};
    \node[] (labF) at (\posF, 2){mapping};

    \node[] (sim1) at (0,-3.25) {\scalebox{0.85}{$X \sim P(X)$}};
    \node[] (sim2) at (0,-3.65) {\scalebox{0.85}{$N \sim P(N)$}};
    \node[] (reg1) at (5,-3.25) {$\hat{E} = \underbrace{(X_2^\top X_2 + \lambda_X)^{-1} X_2^\top Y_2\overbrace{(Y_1^\top Y_1 + \lambda_Y)^{-1} Y_1^\top X_1}^{\text{1) } \hat{X} : \text{ regression from } Y \text{ to } X}}_{\text{2) regression from } X \text{ to } \hat{X}} $};
    \end{tikzpicture}
    \caption{In its linear form, back-to-back regression identifies the subset of factors that suffices to account for multidimensional observations by piping two successive regressions from $Y$ to $X$ and from $X$ to $\hat X$. }
    \label{fig:}
\end{figure}

@@

In the non linear model, $F(EX+N)$ is defined as before, but Y is the result of a non linear transformation of it $$Y=\sigma (F(EX+N))$$

@@

\subsection{Asymptotic behaviour - non linear case}

@@

\section{Experiments - simulated data}
\input{synthetic.tex}

\section{Experiments - real case}
Jean Remi and Maxime territory

@@

\section{Acknowlegements}
Data were provided (in part) by the Donders Institute for Brain, Cognition and Behaviour.

@@

\section{Appendices}

This should hold part of the tests, explanations on simulation, detailed results and stuff on meg data

>>>>

\title{Measuring causal influence with\\ back-to-back regression}

@@

    \node[] (labY) at (\posY, 3){Observations};
    \node[] (labX) at (\posX, 3){Factors};
    \node[] (labE) at (\posE, 3.3){Cause};
    \node[] (labE) at (\posE, 3){selection};
    \node[] (labN) at (\posN, 3){Noise};
    \node[] (labF) at (\posF, 3.3){Cause-effect};
    \node[] (labF) at (\posF, 3){mapping};

    \node[] (labY) at (\posY, 2)   {\color{gray} MEG recordings};
    \node[] (labX) at (\posX, 2)   {\color{gray} stimulus};
    \node[] (labX) at (\posX, 2.3) {\color{gray} features};
    \node[] (labE) at (\posE, 2.3) {\color{gray} causal};
    \node[] (labE) at (\posE, 2)   {\color{gray} features};
    \node[] (labN) at (\posN, 2)   {\color{gray} breathing\ldots};
    \node[] (labF) at (\posN, 2.3) {\color{gray} bloodflow,};
    \node[] (labF) at (\posF, 2)   {\color{gray} MEG helmet};

    \node[] (sim1) at (0,-3.25) {\scalebox{0.85}{$X \sim P(X)$}};
    \node[] (sim2) at (0,-3.65) {\scalebox{0.85}{$N \sim P(N)$}};
    \node[] (reg1) at (5.5,-3.25) {$\hat{E} = \text{Diag}(\underbrace{(X_2^\top X_2 + \Lambda_X)^{-1} X_2^\top Y_2\overbrace{(Y_1^\top Y_1 + \Lambda_Y)^{-1} Y_1^\top X_1}^{\text{1) } \hat{X} : \text{ regression from } Y \text{ to } X}}_{\text{2) regression from } X \text{ to } \hat{X}})$};
    \end{tikzpicture}
    \caption{Back-to-back regression identifies the subset of factors $E_{ii} = 1$ in $X$ that influence some observations $Y$ by 1) regressing from $Y$ to $X$ to obtain $\hat{X}$, and ii) returning the diagonal of the regression coefficients from $X$ to $\hat{X}$.}
    \label{fig:}
\end{figure}

@@

% In the non linear model, $F(EX+N)$ is defined as before, but Y is the result of a non linear transformation of it $$Y=\sigma (F(EX+N))$$

@@

% \subsection{Asymptotic behaviour - non linear case}

\section{Experiments}
\subsection{Synthetic data}

\input{synthetic.tex}

\subsection{Magnetoencephalography data}

@@

@@

% \section{Acknowlegements}
% Data were provided (in part) by the Donders Institute for Brain, Cognition and Behaviour.

@@

%\section{Appendices}
%
%This should hold part of the tests, explanations on simulation, detailed results and stuff on meg data
